### 2016-09-12 draft.tex
.

\begin{equation}
NO_{approx.}(r) = \frac{1}{\sqrt{\frac{1}{NO_{source,num.}^2} + \frac{1}{NO(r)^2}}}
\label{Numeric_Solution_Expression_Trick}
\end{equation}

At the pole $NO(0)$, $NO_{approx.}(0)$ then takes the value $NO_{source,num.}$. On the other hand, for larger values of $r$, the term $\frac{1}{NO_{source,num.}^2}$ becomes negligible compared to $ \frac{1}{NO(r)^2}$, thus $NO_{approx.}(r) \rightarrow NO(r)$ for $r \rightarrow \infty$.

@@

\begin{equation}
NO_{source,num.} = \frac{1-h\sqrt{\frac{\lambda}{\pi D}} K_1\left( h\sqrt{\frac{\lambda}{\pi D}}\right) }{h^2 \lambda}
\label{Numeric_Grid_Bessel_Approx}
\end{equation}

@@

In addition, one needs to account for the boundary conditions used in the network simulation. We simulated the network with Von-Neumann boundary conditions (setting the flux through the boundary to zero) as well as periodic boundaries. Both types can be modelled by extending the neurons' population through spatially shifted and mirrored versions of the base population:

@@

>>>>

\begin{equation}
NO_{approx.}(d) = \frac{1}{\sqrt{\frac{1}{NO_{source,num.}^2} + \frac{1}{NO(d)^2}}}
\label{Numeric_Solution_Expression_Trick}
\end{equation}

At the pole $NO(0)$, $NO_{approx.}(0)$ then takes the value $NO_{source,num.}$. On the other hand, for larger values of $r$, the term $\frac{1}{NO_{source,num.}^2}$ becomes negligible compared to $ \frac{1}{NO(d)^2}$, thus $NO_{approx.}(d) \rightarrow NO(d)$ for $d \rightarrow \infty$.

@@

\begin{equation}
NO_{source,num.} =  r \cdot \frac{1-h\sqrt{\frac{\lambda}{\pi D}} K_1\left( h\sqrt{\frac{\lambda}{\pi D}}\right) }{h^2 \lambda} \equiv r \cdot \psi_{source,num.}
\label{Numeric_Grid_Bessel_Approx}
\end{equation}
with $r$ being the neuron's rate. Equivalently, one can then define
\begin{equation}
\psi_{approx.}(d) \equiv \frac{1}{\sqrt{\frac{1}{\psi_{source,num.}^2} + \frac{1}{\psi (d)^2}}}
\end{equation}

@@

In addition, one needs to account for the boundary conditions used in the network simulation. We simulated the network with Neumann boundary conditions (setting the flux through the boundary to zero) as well as periodic boundaries. Both types can be modelled by extending the neurons' population through spatially shifted and mirrored versions of the base population (see Figure \ref{Bound_Cond_Patches}):

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.5\textwidth]{../../plots/Boundary_Cond_Sketch.png}
\end{center}
\caption{Sketch for patches of copied (and mirrored) positions for periodic (A) and Neumann (B) boundary conditions.}
\label{Bound_Cond_Patches}
\end{figure}

The entries of the operator for periodic boundary conditions $\hat{\psi}_{per.}$ can now calculated by
\begin{equation}
\psi_{ij,per.} = \sum_{n_x,n_y \in \mathbb{Z}} \psi_{approx.} (d(\mathbf{x}_{neur,i},\mathbf{x}_{neur,i} + L \cdot (n_x,n_y)))
\label{Psi_entries_periodic_bound}
\end{equation}
Note that the shift was applied to the second position. Theoretically, $n_x$,$n_y$ is iterated over all integers and in this case it is irrelevant whether to shift the first or the second position. For numerical calculations however, the shift was applied to the second position.

For the Neumann boundary condition, one finds
\begin{align}
\psi_{ij,neum.} &= \sum_{n_x,n_y \in \mathbb{Z}} \psi_{approx.} \left( d(\mathbf{x}_{neur,i},M(\mathbf{x}_{neur,i}) + L \cdot (n_x,n_y)) \right) \label{Psi_entries_neumann_bound} \\
M(\mathbf{x}) &\equiv  
 \begin{pmatrix}
  (-1)^{n_x} & 0\\
  0 & (-1)^{n_y}
 \end{pmatrix}
\mathbf{x} + L \cdot (mod(\left| n_x\right|,2),mod(\left| n_y\right|,2)) \label{Mirror_Operator}
\end{align}

We compared the firing rate distributions acquired from the solution of the random matrix system and those of the full simulated network by means of its standard deviation and skewness.

\begin{figure}
\includegraphics[width=\textwidth]{../../plots/firing_rate_dists/frequ_moments_compare.png}
\caption{Standard deviation and skewness of firing rate distributions for the full spiking network (blue) and the solution of the random matrix model (orange) for Neumann (A,B) and periodic (C,D) boundary conditions.}
\label{frequ_moments_compare}
\end{figure}
